\chapter{Introduction}

\noindent Teaching a computer to synthesize music using deep learning based methods has historically been a difficult task. Audio contains thousands of sound features every second in the time domain that are difficult to accurately teach to a neural network. Even if a network successfully learns how to interpret musical features, the output of models often sound fake or jarring to the listener due to inaccurate pitch and timbre representations and a lack of temporal context.

A subset of this topic is vocal sound synthesis using neural networks. This niche pertains to synthesizing singing and speech sounds using deep learning methods. This has historically proven more difficult than synthesizing instrumental based music due to the complexity of the human voice, with many different vocal modes and features that are difficult to learn through a neural network.

In this paper, the problem of difficulty surrounding synthesizingn the human voice and singing is investigated. A variety of approaches have been proposed to solve this problem, with varying degrees of success, the methods and the results of which are discussed in this paper.

The goal of this paper is to compare the various approaches to vocal sound synthesis, evaluating the merits and limitations of each approach. With the ultimate goal of building on the best of the existing methods further, demonstrating the applicability of the proposed approach.

Many potential applications would be oppened up if a deep learning model could be devised that could accurately learn, understand, and synthesize the fundamental features of music. These uses include many potentially artistic and business applications:

\begin{itemize}
    \item Rapidly generating new music
    \item Pitch transposing a piece of music eg transposing a piece of music down an octave, or up an octave.
    \item Changing room accoustics, eg if a piece of music was played in any echoic room, the model could be used to re-synthesize the same piece of music in an anechoic environment.
    \item Change the singing voice in a particular piece of music, in a similar fashon to deepfakes.
    \item Musical remixes of existing songs with different singers.
    \item Potentialy brand new forms of artistic expression, with a neural network perhaps being able to produce vocal features that are impossible to create naturally.
\end{itemize}

\input{introduction/aims_and_objectives.tex}

\input{introduction/methodology.tex}

% TODO: Move to literature review or later sections

%Additionally the model could be accurately trained on smaller datasets with smaller model sizes, reducing the training cost and time assocciated with certain model accuracy.
%
%Most DDSP research to date has been focused on modelling of musical instruments, this is due to their relative constant timbre characteristic over an entire instrument, making it easier to model.